SaPaFigures

### 2022-03-16 R/PaperFigures.Rmd
Added the updated color palete, changed the wtED, added plotAggCoreMut

PlotBiomassPointsMutants<- function(){
  ggplot()+
    geom_jitter(data = BiomassDataMut,aes(x=Species,y=Biomass, color = Strain),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = biomassMutData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Strain)
                ,width = .4, size=.5,position = position_dodge(width = .9))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
                  limits = c(1, 10e7), expand = expand_scale(mult = c(0, 0)))+
    scale_color_brewer(palette = "Set1",
      labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+

@@

@@

PlotHistSumFinalStrainsViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){#doesn't include region
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                scale = "width", trim = F,
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]]))+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=5, position = position_dodge(width = 1) )+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .8,position = position_dodge(width = 1) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    scale_color_brewer(palette = "Set1",
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")), color = "Condition")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}#only difference between these two should be "scale_color_grey
PlotHistSumFinalStrainsViolin(HistReplicateSummary%>% filter(Culture =="co"),
            HistConditionSummary%>% filter(Culture =="co"),
            HistCondRegionSum%>% filter(Culture =="co"),
            "NormalizedFrequency","Strain")

#####
#Figure 2C
#Aggregation inner vs outer region
#####
PlotAggCore<-function(rep.df,region.df, y_var, title,colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=Region,y=.data[[y_var]], color =.data[[colorStrain]]),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
    geom_errorbar(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=Region,ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    #geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
     #          aes(x=Region,y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    ggtitle(title)+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

#Figure 2D
##Marvin suggested doing the enrichment distance for those samples, but I guess there is nothing to compare, unless I do core vs edge
##ggplot code from PropOc Data 3D
PlotwtED<-function(){
df1<-pOEnrMetaStatsRegion %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
df2<-pOEnrMetaClean %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
  ggplot()+
    geom_errorbar(data = df1,aes(y=meanED,ymax=meanED,ymin=meanED, group = Region,x = Condition),
                    position = position_dodge(width = .75), width = 0.5)+
    geom_point(data = df2,aes(y=WmeanDist,x = Condition, shape = Region),position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
    labs(y = expression("Enrichment distance ("*mu*"m)"), x = "") +
    scale_color_grey()+
    scale_x_discrete(labels = c(""))+
    scale_shape_manual(values=c(16, 1))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
    panel_border() 
}

PlotwtED()

#Figure 2E
PlotEDvsDensityFinal<-function(df, yAxis,tittle){
  ggplot()+
    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], shape =Region ),size=4)+
    #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
    geom_abline(intercept = 10.683, slope = 44.416, color = "Black")+
    #geom_text(x=.3, y=30, label= bquote(paste("R"^2*"=0.3368")))+
    #geom_text(x=.3, y=10, label= "bl")+
    annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
    #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
    #geom_abline(intercept = 9.519, slope = 50.800, color = "Red")+
    labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
    scale_shape_manual(values=c(16, 1))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotEDvsDensityFinal(EdSlice %>% filter(Strain == "wt"), "TotalRatio","")

>>>>

PlotBiomassPointsMutants<- function(){
  ggplot()+
    geom_jitter(data = BiomassDataMut,aes(x=Species,y=Biomass, color = Strain),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = biomassMutData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Strain)
                ,width = .4, size=.5,position = position_dodge(width = .9))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
                  limits = c(1, 10e7), expand = expand_scale(mult = c(0, 0)))+
    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
      labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+

@@

PlotHistSumFinalViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                scale = "width", trim = F,
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]]))+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .5,position = position_dodge(width = .75) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotHistSumFinalViolin(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            HistConditionSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            "NormalizedFrequency", "Culture")

@@

PlotHistSumFinalStrainsViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){#doesn't include region
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                scale = "width", trim = T,
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]]))+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=5, position = position_dodge(width = 1) )+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .8,position = position_dodge(width = 1) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")), color = "Condition")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}#only difference between these two should be "scale_color_grey
PlotHistSumFinalStrainsViolin(HistReplicateSummary%>% filter(Culture =="co"),
            HistConditionSummary%>% filter(Culture =="co"),
            HistCondRegionSum%>% filter(Culture =="co"),
            "NormalizedFrequency","Strain")

#####
#Figure 2D
#Aggregation inner vs outer region
#####
PlotAggCore<-function(rep.df,region.df, y_var, title,colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=.data[[colorStrain]],y=.data[[y_var]], shape = Region, color =.data[[colorStrain]]),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3, show.legend = F)+
    geom_errorbar(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=.data[[colorStrain]],ymin=.data[[y_var]],ymax=.data[[y_var]], group =Region),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    #geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
     #          aes(x=Region,y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_x_discrete(labels = c("Mono-culture","Co-culture"))+
    ggtitle(title)+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

PlotAggCoreMut<-function(rep.df,region.df, y_var, title,colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=Region,y=.data[[y_var]], shape = Region, color =.data[[colorStrain]]),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
    geom_errorbar(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=Region,ymin=.data[[y_var]],ymax=.data[[y_var]], group =Strain),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    #geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
     #          aes(x=Region,y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    ggtitle(title)+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotAggCoreMut(plankAggHistRep%>% filter(Culture=="co") %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "", "Strain", "Species")

#Figure 2E
## Enrichment distance
#####
##Marvin suggested doing the enrichment distance for those samples, but I guess there is nothing to compare, unless I do core vs edge
##ggplot code from PropOc Data 3D
PlotwtED<-function(){
df1<-pOEnrMetaStatsRegion %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
df2<-pOEnrMetaClean %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
  ggplot()+
    geom_errorbar(data = df1,aes(y=meanED,ymax=meanED,ymin=meanED, group = Region,x = Condition),
                    position = position_dodge(width = .75), width = 0.5)+
    geom_point(data = df2,aes(y=WmeanDist,x = Condition, shape = Region),position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("S. aureus") %->% italic("S. aureus ")))), x = "") +
    scale_color_grey()+
    scale_x_discrete(labels = c(""))+
    scale_shape_manual(values=c(16, 1))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
    panel_border() 
}

PlotwtED()
#In this case, i want an actual x axis, but the top may work for reference
PlotwtED2<-function(){
df1<-pOEnrMetaStatsRegion %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
df2<-pOEnrMetaClean %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
  ggplot()+
    geom_errorbar(data = df1,aes(y=meanED,ymax=meanED,ymin=meanED, x = Region), width = .5)+
    geom_point(data = df2,aes(y=WmeanDist,x = Region, shape = Region),position = position_jitter(height = 0, width = .2),size=3, show.legend = F)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("S. aureus") %->% italic("S. aureus ")))), x = "") +
    scale_color_grey()+
    scale_shape_manual(values=c(16, 1))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
    panel_border() 
}

PlotwtED2()
#####
#Figure 2F
PlotEDvsDensityFinal<-function(df, yAxis,tittle){
  ggplot()+
    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], shape =Region ),size=4)+
    #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
    geom_abline(intercept = 10.683, slope = 44.416, color = "Black")+
    #geom_text(x=.3, y=30, label= bquote(paste("R"^2*"=0.3368")))+
    #geom_text(x=.3, y=10, label= "bl")+
    annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
    #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
    #geom_abline(intercept = 9.519, slope = 50.800, color = "Red")+
    labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
    scale_shape_manual(values=c(16, 1))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotEDvsDensityFinal(EdSlice %>% filter(Strain == "wt"), "TotalRatio","")
